%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Intership} % Job title
    {International Institute for Computational Science and Engineering (ICSE)} % Organization
    {Hanoi, Vietnam} % Location
    {2015-2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learn about Cloud Computing \& OpenStack.}
        \item {Work with Linux distros: Ubuntu, CentOS \& RedHat.}
        \item {Deploy OpenStack High Availability with HAProxy \& Pacemaker in RedHat servers.}
        \item {Investigate about Container \& Docker.}
        \item {Investigate \& participate in Cloud Abstract Layer (CAL) Project tutored by Ph.D Binh Minh Nguyen (HUST) \& MSc Hieu Le Quang. Now, CAL is available in Pypi. (https://pypi.python.org/pypi/calplus/)}
        \item {Investigate \& participate in Bio-Informatics Management Interface (BIMI) Project tutored by Ph.D Binh Minh Nguyen (HUST) \& MSc Hieu Le Quang.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Part time Developer} % Job title
    {Vega Corp.} % Organization
    {Hanoi, Vietnam} % Location
    {12/2016 - 04/2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research \& Develop (RnD) OpenStack in production environment.}
        \item {Develop an OpenStack automation deployment tool (shell scripts).}
        \item {Setup Ubuntu \& CentOS mirror repositories.}
        \item {Virtualization, Physical \& OpenStack monitoring with Zabbix.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Fujitsu Vietnam} % Organization
    {Hanoi, Vietnam} % Location
    {06/2017 - 03/2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Upstream OpenStack contributor, strongly focus on Container related projects - Zun, Kolla, Kuryr.}
      	\item {Join OpenStack community, communicate with other OpenStack's contributors around the world.}
        \item {Investigate \& deploy Kubernetes.}
        \item {Fix Bugs, implement Blueprint for OpenStack Zun, Kuryr-libnetwork.}
        \item {Apply Heat rolling upgrade strategy in CI/CD gates.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Viettel Group} % Organization
    {Hanoi, Vietnam} % Location
    {03/2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deploy OpenStack cluster using Kolla.}
        \item {Upstream OpenStack \& Prometheus contributor.}
        \item {Work with Monitor \& Logging set of tools (Prometheus, EFK stack).}
        \item {Investigate \& apply OpenStack strategy using Heat \& Telemetry projects.}
        \item {Investigate OpenStack autohealing.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
